CoIL Challenge Submission

### 2019-11-06 final project/Manuscript.Rmd
More work on final

---
title             : "Fall 2019 DATA 621 Final Project"
shorttitle        : "Arnouts et al. Final Project"
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "CUNY School of Professional Studies"
authornote: |
  MS in Data Science Students
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf
---

@@

# Introduction
```{r eval=FALSE, echo=FALSE}
#Describe the background and motivation of your problem.
```
Busineses use data science to extract insight from data.  It has many practical business applications.  The CoIL Challenge showcases the power data science can bring to bear on fundamental business problems.

The CoIL Challenge was a datamining competition organized by the the Computational Intelligence and Learning Cluster. It was held in the period of March-May 2000.  The COIL Challenge had two tasks:

@@

In total 43 solutions were submitted. The winners of the challenge were Charles Elkan for the prediction task and Nick Street and YongSeog Kim for the description task.

In this paper we set out to complete the COIL Challenge ourselves using a logistic regression classifier. **SUMARISE FINDINGS**

@@

@@

- Supplemental tables and/or figures.
- R statistical programming code.

>>>>

---
title             : "CoIL Challenge Submission"
shorttitle        : "CoIL Challenge Submission"
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "CUNY School of Professional Studies"
authornote: |
  MS in Data Science Students
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    #citation_package: natbib #biblatex
  html_document: default
---

@@

# Introduction

```{r eval=FALSE, echo=FALSE}
#Describe the background and motivation of your problem.
```
Busineses use data science to extract insight from data.  It has many practical business applications.  The Computational Intelligence and Learning (CoIL) Challenge showcases the power data science can bring to bear on fundamental business problems.

The CoIL Challenge was a datamining competition held from March 17 to May 8 in 2000.  Participants could:

@@

In total 147 participants registered and 43 submitted solutions [@Putten-2000]. The winners of the challenge were Charles Elkan for the prediction task and Nick Street and YongSeog Kim for the description task.

In this paper we set out to complete the prediction part of the COIL Challenge ourselves using a logistic regression classifier. **SUMARISE FINDINGS**

@@

The maximum number of policyowners that could be found was 238, the winning model selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks)and 118 (linear!) policy owners. [@Putten-2000]

@@

- Supplemental tables and/or figures.

## R statistical programming code.

```{r source, code=readLines("CoIL.R")}
```

### 2019-11-06 final project/Manuscript.tex
More work on final

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Fall 2019 DATA 621 Final Project},
            pdfauthor={Corey Arnouts, Adam Douglas, Jason Givens-Doyle, \& Michael Silva},
            pdfkeywords={CoIL Challenge, Logistic Regression},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Fall 2019 DATA 621 Final Project}
    \author{Corey Arnouts\textsuperscript{1}, Adam Douglas\textsuperscript{1}, Jason Givens-Doyle\textsuperscript{1}, \& Michael Silva\textsuperscript{1}}
    \date{}

\shorttitle{Arnouts et al. Final Project}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} CUNY School of Professional Studies}
\keywords{CoIL Challenge, Logistic Regression\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

@@

Busineses use data science to extract insight from data. It has many practical business applications. The CoIL Challenge showcases the power data science can bring to bear on fundamental business problems.

The CoIL Challenge was a datamining competition organized by the the Computational Intelligence and Learning Cluster. It was held in the period of March-May 2000. The COIL Challenge had two tasks:

@@

In total 43 solutions were submitted. The winners of the challenge were Charles Elkan for the prediction task and Nick Street and YongSeog Kim for the description task.

In this paper we set out to complete the COIL Challenge ourselves using a logistic regression classifier. \textbf{SUMARISE FINDINGS}

@@

@@

We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018) for all our analyses.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

@@

\begin{itemize}
\tightlist
\item
  Supplemental tables and/or figures.
\item
  R statistical programming code.
\end{itemize}

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={CoIL Challenge Submission},
            pdfauthor={Corey Arnouts, Adam Douglas, Jason Givens-Doyle, \& Michael Silva},
            pdfkeywords={CoIL Challenge, Logistic Regression},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{CoIL Challenge Submission}
    \author{Corey Arnouts\textsuperscript{1}, Adam Douglas\textsuperscript{1}, Jason Givens-Doyle\textsuperscript{1}, \& Michael Silva\textsuperscript{1}}
    \date{}

\shorttitle{CoIL Challenge Submission}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} CUNY School of Professional Studies}
\keywords{CoIL Challenge, Logistic Regression\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother

@@

Busineses use data science to extract insight from data. It has many practical business applications. The Computational Intelligence and Learning (CoIL) Challenge showcases the power data science can bring to bear on fundamental business problems.

The CoIL Challenge was a datamining competition held from March 17 to May 8 in 2000. Participants could:

@@

In total 147 participants registered and 43 submitted solutions (Putten, Ruiter, \& Someren, 2000). The winners of the challenge were Charles Elkan for the prediction task and Nick Street and YongSeog Kim for the description task.

In this paper we set out to complete the prediction part of the COIL Challenge ourselves using a logistic regression classifier. \textbf{SUMARISE FINDINGS}

@@

The maximum number of policyowners that could be found was 238, the winning model selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks)and 118 (linear!) policy owners. (Putten et al., 2000)

@@

We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{\}papaja} {[}@\}R-papaja{]} for all our analyses.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Putten-2000}{}%
Putten, P., Ruiter, M., \& Someren, M. (2000). CoIL challenge 2000 tasks and results: Predicting and explaining caravan policy ownership.

@@

\begin{itemize}
\tightlist
\item
  Supplemental tables and/or figures.
\end{itemize}

\hypertarget{r-statistical-programming-code.}{%
\subsection{R statistical programming code.}\label{r-statistical-programming-code.}}
